### 2015-07-21 src/misc/s4_aboutme.tex
Updated after feedback
Fixed minor bugs in PDF
Updated about me.

\clearpage
\pagestyle{empty}

@@

Ivar Clemens was born on the 2nd of June 1984 in Boxtel, The Netherlands. He started his studies in 2000 at the Koning Willem 1 College where he obtained a degree in Industrial Automation. He then started work on a master's degree in Biology at the Radboud University Nijmegen. As part of this master's degree Ivar did his research internship on the \emph{integration of pre- and post-vergence target distance cues} with Pieter Medendorp at the Nijmegen Institute for Cognition and Information (NICI, later renamed to the Donders Centre for Cognition). Ivar then switched to the Donders Centre for Cognitive Neuro-imaging (DCCN) for another research internship. This time he worked with Ole Jensen and Saskia Haegens on \emph{homeostatic plasticity in the somatosensory cortex}. After completing his master's degree in 2009, Ivar started his PhD project at he Donders Centre for Cognition. The results of this PhD project are contained within this thesis. As of [month] 2015, Ivar is employed at [institute] where he works on [topic].

>>>>

\clearpage
%\pagestyle{empty}

@@

Ivar Clemens was born in 1984 in Boxtel, the Netherlands. After obtaining a degree in Industrial Automation at the Koning Willem 1 College in 's-Hertogenbosch, he started a master's degree in Biology at the Radboud University in Nijmegen, the Netherlands. In 2008 Ivar did his first research internship on the \emph{integration of pre- and post-vergence target distance cues} with Pieter Medendorp at the Nijmegen Institute for Cognition and Information (NICI, later renamed to the Donders Centre for Cognition). Ivar then switched to the Donders Centre for Cognitive Neuro-imaging (DCCN) for his second research internship. This time he worked with  Ole Jensen and Saskia Haegens on \emph{homeostatic plasticity in the somatosensory cortex}. He obtained his master's degree in 2009 and started his PhD research under the supervision of Pieter Medendorp and Luc Selen at the Donders Centre for Cognition. During his PhD he worked on the integration of sensory signals in spatial orientation and self-motion perception. In January 2015 he joined the group dynamics lab at the Champalimaud Centre for the Unknown in Lisbon, Portugal.
